\documentclass{sice-si}

\usepackage{bm} %bm使えるように
\usepackage{tabularx} % プリアンブルに追加
\usepackage{array} % プリアンブルに追加

\usepackage{svg}
\usepackage{fontspec}

\def\LuaLaTeX{Lua\LaTeX}
\def\upLaTeX{up\LaTeX}
\def\pTeX{p\TeX}
\def\SICEcls{sice.cls}

\newcommand{\TeXEngine}{unknown}
\ifluatex
    \renewcommand{\TeXEngine}{\LuaLaTeX}
\else
    \ifuptex
        \renewcommand{\TeXEngine}{\upLaTeX}
    \fi
\fi

\addbibresource{references.bib}

% タイトルと著者名
\title{\textbf{時定数と膜抵抗の動的変動による \\ 広範な時間スケールに頑健なSpiking Neural Networkの構築}} % 和文タイトル
\name{○平野 貴也 (東北大学), 沓澤 京 (東北大学), 大脇 大 (東北大学), 林部 充宏 (東北大学)} % 著者名
\etitle{A Spiking Neural Network Robust to a Wide Range of Time Scales \\ through Dynamic Variations in Time Constants and Membrane Resistance} % 英文タイトル
\ename{○Takaya HIRANO (Tohoku University), Kyo KUTSUZAWA (Tohoku University),\\ Dai OWAKI (Tohoku University), and Mitsuhiro HAYASHIBE (Tohoku University)}	%著者名（英）

\begin{document}
% アブストラクト
\abst{
    Spiking Neural Networks (SNNs) are neural networks that are more similar to the brain's neural circuits than Artificial Neural Networks (ANNs).
    By using the brain's sparsity, SNNs improve memory efficiency and reduce energy use during computation, making them an important type of neural network.
    SNNs are similar to brain neuron dynamics by processing spikes of 0 or 1.
    This allows SNNs to excel at processing time-series information.
    However, most SNNs use the Leaky Integrate-and-Fire (LIF) model, which has a fixed time constant, limiting their ability to represent different temporal characteristics.
    Recent studies have introduced trainable time constants in LIF models, improving representation.
    Despite these improvements, training still requires data with various time scales.
    This study proposes a SNN with dynamically changing parameters, including time constants, allowing it to adapt to multiple time scales by training on a single time scale.
    The proposed method maintains high accuracy with time-series data of different time scales and is robust against changes in time scales within the input data.
}

\date{} % 日付を出力しない
% タイトルの出力
\maketitle

\thispagestyle{empty}
\pagestyle{empty}



% >> 内容 >>
% \input{sections/sample.tex}
\input{sections/section1/section1.tex}
\input{sections/section2/section2.tex}
\input{sections/section3/section3.tex}
\input{sections/section4/section4.tex}
\input{sections/section5/section5.tex}
\input{sections/section6/section6.tex}
% >> 内容 >>

% \bibliographystyle{junsrt} %junsrt → 引用順
\printbibliography[title=参考文献]

\end{document}